### 2016-03-10 docs/ms_communitySynchrony.Rmd
updates theory discussion and prediction table caption

In grasslands, most empirical studies have focused on whether species synchrony is primarily an outcome of species-specific responses to environmental conditions [@Hautier2014] or competition [@Gross2014].
Even beyond grassland studies, whether competition or environmental responses drive compensatory dynamics remains controversial [reviewed in @Gonzalez2009].
In part, controversy remains because quantifying the relative strengths of each driver on the degree of synchrony from community time series [e.g., @Houlahan2007] is impossible.
This is because an unbiased null expectation for synchrony does not exist [@Loreau2008a] and observed synchrony can arise from non-unique combinations of factors [@Ranta2008].
For example, weak synchrony could reflect positive environmental correlations (synchronizing effect) offset by strong competition (desynchronizing effect), or negative environmental correlations and weak competition.

@@

@@

Across the five communities, our limiting case prediction of community-wide synchrony when only environmental stochasticity is operating ($\mathcal{M}_E$) best matched observed synchrony for per capita growth rates (Fig. 1).
The regression line between observed growth rate synchrony and predicted growth rate synchrony under prediction $\mathcal{M}_E$ was the only one whose slope and intercept were not significantly different from zero (*P* = 0.88) and one (*P* = 0.87), respectively (Supplementary Information X).
The regression line between observed and predicted growth rates under prediction $\mathcal{M}_D$ (demographic stochasticity only) had an intercept and slope significantly different from zero and one, respectively (Fig. 1).

@@

### Simulations support theoretical predictions

### Demographic stochasticity decreases synchrony
Demographic stochasticity is able to partially counteract the synchronizing effects of environmental fluctuations and interspecific interactions on per capita growth rates, but only when populations are small (Fig. 3), in agreement with theory [@Loreau2008a].
Even in small populations, however, demographic stochasticity is not a strong enough force to induce independent fluctuations (Fig. 3).
These results confirm the theoretical argument by @Loreau2008a that independent fluctuations among interacting species in a non-constant environment should be rare.
Only in the Idaho community does synchrony of per capita growth rates approach independent fluctuations (1/*S*, where *S* is the number of specuies) in a non-constant environment (Fig. 3).
This is most likely due to the strong effect of demographic stochasticity on the shrub *Artemisia tripartita* since even a 5 $\text{m}^2$ quadrat would only contain a few individuals of that species.

@@

The insensitivity of species synchrony to model perturbations in the Idaho community challenges the consistency of our results.
Idaho's outlier status is due to its functional diversity.
In fact, when we removed the shrub (*Artemisia tripartita*) from our analyses, results from the Idaho data set conformed with results from all other sites: removing environmental stochasticity caused a significant reduction in species synchrony (Fig. SX).
Our main results for Idaho (Fig. 2), with *A. tripartita* included, demonstrate how the processes that determine species synchrony interact in complex ways.
*A. tripartita* has a facilitative effect on each grass species across all vital rates, except for a small competitive effect on *H. comata*'s survival probability (Tables SX, SX, SX).
At the same time, all the perennial grasses have negative effects on each other for each vital rate (Tables SX, SX, SX).
Thus, interspecific interactions play a relatively large role in determining synchrony in Idaho, but only when *A. tripartita* is at equilibrium abundance.
The removal of environmental variation causes a decrease in the abundance of *A. tripartita* and, in turn, a weakening of the overall effect of competition on species synchrony.
This would explain why synchrony actually increases when we remove environmental fluctuations in Idaho (Fig. 2).

@@

pred_cap <- "Predicted and simulated synchrony of per capita growth rates under the two limiting cases."
print(xtable(pred_table, caption = pred_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE,
      size="normalsize")
```

>>>>

In grasslands, most empirical studies have focused on whether species synchrony is primarily an outcome of species-specific responses to environmental conditions [@Hautier2014] or competition [@Gross2014].
Even beyond grassland studies, whether competition or environmental responses drive compensatory dynamics remains controversial [reviewed in @Gonzalez2009].
In part, controversy remains because quantifying the relative strengths of each driver on the degree of synchrony from community time series [e.g., @Houlahan2007] is impossible.
This is because an unbiased null expectation for synchrony does not exist [@Loreau2008a] and observed synchrony can arise from non-unique combinations of factors [@Ranta2008].
For example, weak synchrony of population abundances could reflect positive environmental correlations (synchronizing effect) offset by strong competition (desynchronizing effect), or negative environmental correlations and weak competition.

@@

Qualitative predictions here...?

@@

Across the five communities, our limiting case predictions closely matched synchrony from simulations designed to test each prediction (Table 3).
The correlation between our analytical predictions and simulated synchrony was 0.97 for $\phi_{R,\mathcal{M}_D}$ and 0.997 for $\phi_{R,\mathcal{M}_E}$.
The largest difference between predicted and simulated synchrony was 0.05 in New Mexico for $\phi_{R,\mathcal{M}_D}$ (Table 3).

@@

### Simulations support theoretical predictions
Our theoretical predictions were derived from a relatively simple model of population dynamics and required several simplifying assumptions.
Yet, our theoretical predictions were strongly supported by our empirically-based model simulations of natural plant communities (Table 3).
Such a close match between our analytical predictions and the simulation results should inspire confidence in the ability of simple models to inform our understanding of species synchrony.
The theoretical population dynamical model we used here also successfully predicted ecosystem stability in several biodiversity-ecosystem function experiments [@DeMazancourt2013a].
Thus, there is accumulating evidence, now from experimental and observational studies, that the population dynamical approach is an extremely useful modeling framework for linking population dynamics to community and ecosystem level properties [@Loreau2010].

### Demographic stochasticity decreases synchrony
Demographic stochasticity is able to partially counteract the synchronizing effects of environmental fluctuations and interspecific interactions on per capita growth rates, but only when populations are small (Fig. 3), in agreement with theory [@Loreau2008a].
Even in small populations, however, demographic stochasticity is not a strong enough to completely counteract the synchronizing effects of environmental fluctuations and induce independent species fluctuations (Fig. 3).
These results confirm the theoretical argument by @Loreau2008a that independent fluctuations among interacting species in a non-constant environment should be rare.
Only in the Idaho community does synchrony of per capita growth rates approach independent fluctuations (1/*S*, where *S* is the number of specuies) in a non-constant environment (Fig. 3).
This is most likely due to the strong effect of demographic stochasticity on the shrub *Artemisia tripartita* since even a 5 $\text{m}^2$ quadrat would only contain a few individuals of that species.

@@

The insensitivity of species synchrony to model perturbations in the Idaho community challenges the consistency of our results.
However, Idaho's outlier status is soley due to its functional diversity.
When we removed the shrub (*Artemisia tripartita*) from our analyses, results from the Idaho data set conformed with results from all other sites: removing environmental stochasticity caused a significant reduction in species synchrony (Fig. SX).
Our main results for Idaho (Fig. 2), with *A. tripartita* included, demonstrate how the processes that determine species synchrony interact in complex ways.
*A. tripartita* has a facilitative effect on each grass species across all vital rates, except for a small competitive effect on *H. comata*'s survival probability (Tables SX, SX, SX).
At the same time, all the perennial grasses have negative effects on each other for each vital rate (Tables SX, SX, SX).
We know synchrony is affected by interspecific competition [@Loreau2008a], but how facilitative effects manifest themselves is unknown.
The interaction of facilitation and competition is clearly capable of having a large effect on species synchrony, and future theoretical efforts should aim to include a wider range of species interactions.

@@

pred_cap <- "Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\\phi_{R,\\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\\phi_{R,\\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\\mathcal{M}_D$)."
print(xtable(pred_table, caption = pred_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE,
      size="normalsize")
```
